|

### 2022-07-20 Presentations/ISBE2022.Rmd
New presentation for ISBE2022

---
title: | 
    | Learning can mediate the evolution of 
    | (cheap and costly) signals of quality
author: "Andrés Quiñones PhD."
bibliography: ../SocialMorphCue.bib
date: | 
    | 
    | 
    | Genes as environment - AGA2020 virtual symposium
    | November 17 - 2020
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
    \usepackage{xcolor}
---

@@

| ![Red1](../Images/redouan.jpg){width=33%} | ![Olle](../Images/olof-leimar.png){width=23%} | ![Daniel](../Images/danielcadena.jpg){width=32%}  |
| :---:        |    :----:   |    :---: |
| *R. Bshary* |*O. Leimar*|*D. Cadena*|

![unine](../Images/UNINE_cmjn.jpg){width=35%}
![uniandes](../Images/logo_largo.png){width=45%}

>>>>

---
title: | 
    | Learning can mediate the evolution of 
    | (cheap and costly) signals of quality
author: "Andrés Quiñones"
bibliography: ../SocialMorphCue.bib
date: | 
    | 
    | 
    | ISBE - Stockholm 2022
    | August 2 - 2020
output: 
    beamer_presentation: 
      fig_caption: yes
      keep_tex: yes
header-includes: 
    \usepackage{float}
    \usepackage{multicol}
    \usepackage{amsmath} 
    \usepackage{graphicx}
    \usepackage{array}
    \usepackage{xcolor}
---

@@

 ![Red1](../Images/redouan.jpg){width=40%} |  ![Daniel](../Images/danielcadena.jpg){width=55%} |
 :---: | :---:|
 *R. Bshary* |*D. Cadena*|
 ![unine](../Images/UNINE_cmjn.jpg){width=30%} | ![uniandes](../Images/logo_largo.png){width=30%} |

### 2022-07-20 Presentations/ISBE2022.tex
New presentation for ISBE2022

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{lmodern}
\usepackage{amssymb,amsmath}
\usepackage{ifxetex,ifluatex}
\ifnum 0\ifxetex 1\fi\ifluatex 1\fi=0 % if pdftex
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones PhD.},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{longtable,booktabs}
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx,grffile}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor}

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones PhD.}
\date{Genes as environment - AGA2020 virtual symposium\\
November 17 - 2020}

@@

\begin{frame}{Acknowledgements}
\protect\hypertarget{acknowledgements}{}

\begin{longtable}[]{@{}ccc@{}}
\toprule
\includegraphics[width=0.33\textwidth,height=\textheight]{../Images/redouan.jpg}
&
\includegraphics[width=0.23\textwidth,height=\textheight]{../Images/olof-leimar.png}
&
\includegraphics[width=0.32\textwidth,height=\textheight]{../Images/danielcadena.jpg}\tabularnewline
\midrule
\endhead
\emph{R. Bshary} & \emph{O. Leimar} & \emph{D. Cadena}\tabularnewline
\bottomrule
\end{longtable}

\includegraphics[width=0.35\textwidth,height=\textheight]{../Images/UNINE_cmjn.jpg}
\includegraphics[width=0.45\textwidth,height=\textheight]{../Images/logo_largo.png}

\end{frame}

\begin{frame}{Social interactions}
\protect\hypertarget{social-interactions}{}

\begin{block}{The need to match partners with actions}

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \end{center}

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/dominance} \end{center}

\end{block}

\end{frame}

\begin{frame}{The effect of communication}
\protect\hypertarget{the-effect-of-communication}{}

\begin{block}{Badge of status}

\begin{center}\includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_strong} \includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_weak} \end{center}

\end{block}

\end{frame}

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals}{}

\begin{block}{The handicap principle}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/Amotz_Zahavi_profile} \includegraphics[height=0.35\textheight]{../Images/sexualSelection} \includegraphics[height=0.35\textheight]{../Images/Grafen} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-4-1} \end{center}

(Zahavi 1975; Grafen 1990)

\end{block}

\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_0} \end{center}

\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-1}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_1} \end{center}

\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-2}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_2} \end{center}

\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-3}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_3} \end{center}

\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-4}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_5} \end{center}

\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-5}{}

\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{../Images/learn_cartoon_6} \end{center}

\end{frame}

\begin{frame}{A model of communication in animal conflict}
\protect\hypertarget{a-model-of-communication-in-animal-conflict}{}

\vspace{-0.3cm}

\begin{block}{Conflict}

\vspace{0.3cm}
\begin{columns}
\column{0.5\linewidth}
hawk-dove game
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.2cm} | >{\centering\arraybackslash}p{2.5cm} | >{\centering\arraybackslash}p{0.8cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-17-1} \end{center}

@@

\pause

\end{block}

\begin{block}{Communication}

\begin{columns}[T]

@@

\begin{center}\includegraphics[width=0.5\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-18-1} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-19-1} \end{center}

\end{block}

\end{frame}

\begin{frame}{Learning under honest signalling}
\protect\hypertarget{learning-under-honest-signalling}{}

\begin{center}\includegraphics[width=1\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn} \end{center}

\end{frame}

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}

\end{frame}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status}{}

\begin{block}{Individual replicates: no badges}

\begin{center}\includegraphics[height=0.9\textheight]{../Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}

\end{block}

\end{frame}

\begin{frame}{The evolution of cheap badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status}{}

\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000} \end{center}

\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized}{}

\vspace{-1cm}

\begin{block}{The peaceful, the aggressive and the clever}

\begin{itemize}
\tightlist
\item
  Learning initial conditions
\end{itemize}

\includegraphics[width=0.45\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn}
\includegraphics[width=0.45\linewidth]{GenesAsEnviron_files/figure-beamer/unnamed-chunk-24-2}

\end{block}

\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-1}{}

\begin{block}{The peaceful, the aggressive and the clever}

\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_1}

\end{block}

\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-2}{}

\begin{block}{The peaceful, the aggressive and the clever}

\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_}

\end{block}

\end{frame}

\begin{frame}{Take-home messages}
\protect\hypertarget{take-home-messages}{}

\begin{block}{Costly signals}

\begin{itemize}
\tightlist
\item
  Learning can mediate costly signals
\end{itemize}

\end{block}

\begin{block}{Cheap signals}

\begin{itemize}
\tightlist
\item
  Learning mediates the evolution of polymorphisms with ``honest'' and
  ``dishonest'' individuals
\item
  Cheap signals depend on the innate level of aggression (before
  learning) of individuals
\end{itemize}

\end{block}

\end{frame}

\begin{frame}{Questions?}
\protect\hypertarget{questions}{}

\begin{center}\includegraphics[height=0.8\textheight]{../Images/BizarroParrot} \end{center}

\end{frame}

\begin{frame}{References}
\protect\hypertarget{references}{}

\hypertarget{refs}{}
\leavevmode\hypertarget{ref-grafen_Biological_1990}{}%
Grafen, Alan. 1990. ``Biological Signals as Handicaps.'' \emph{Journal
of Theoretical Biology} 144 (4): 517--46.
\url{https://doi.org/10.1016/S0022-5193(05)80088-8}.

\leavevmode\hypertarget{ref-zahavi_Mate_1975}{}%
Zahavi, Amotz. 1975. ``Mate Selection-A Selection for a Handicap.''
\emph{Journal of Theoretical Biology} 53 (1): 205--14.
\url{https://doi.org/10.1016/0022-5193(75)90111-3}.

\end{frame}

>>>>

% Options for packages loaded elsewhere
\PassOptionsToPackage{unicode}{hyperref}
\PassOptionsToPackage{hyphens}{url}
%
\documentclass[
  ignorenonframetext,
]{beamer}
\usepackage{pgfpages}
\setbeamertemplate{caption}[numbered]
\setbeamertemplate{caption label separator}{: }
\setbeamercolor{caption name}{fg=normal text.fg}
\beamertemplatenavigationsymbolsempty
% Prevent slide breaks in the middle of a paragraph
\widowpenalties 1 10000
\raggedbottom
\setbeamertemplate{part page}{
  \centering
  \begin{beamercolorbox}[sep=16pt,center]{part title}
    \usebeamerfont{part title}\insertpart\par
  \end{beamercolorbox}
}
\setbeamertemplate{section page}{
  \centering
  \begin{beamercolorbox}[sep=12pt,center]{part title}
    \usebeamerfont{section title}\insertsection\par
  \end{beamercolorbox}
}
\setbeamertemplate{subsection page}{
  \centering
  \begin{beamercolorbox}[sep=8pt,center]{part title}
    \usebeamerfont{subsection title}\insertsubsection\par
  \end{beamercolorbox}
}
\AtBeginPart{
  \frame{\partpage}
}
\AtBeginSection{
  \ifbibliography
  \else
    \frame{\sectionpage}
  \fi
}
\AtBeginSubsection{
  \frame{\subsectionpage}
}
\usepackage{amsmath,amssymb}
\usepackage{lmodern}
\usepackage{iftex}
\ifPDFTeX
  \usepackage[T1]{fontenc}
  \usepackage[utf8]{inputenc}
  \usepackage{textcomp} % provide euro and other symbols
\else % if luatex or xetex
  \usepackage{unicode-math}
  \defaultfontfeatures{Scale=MatchLowercase}
  \defaultfontfeatures[\rmfamily]{Ligatures=TeX,Scale=1}
\fi
% Use upquote if available, for straight quotes in verbatim environments
\IfFileExists{upquote.sty}{\usepackage{upquote}}{}
\IfFileExists{microtype.sty}{% use microtype if available
  \usepackage[]{microtype}
  \UseMicrotypeSet[protrusion]{basicmath} % disable protrusion for tt fonts
}{}
\makeatletter
\@ifundefined{KOMAClassName}{% if non-KOMA class
  \IfFileExists{parskip.sty}{%
    \usepackage{parskip}
  }{% else
    \setlength{\parindent}{0pt}
    \setlength{\parskip}{6pt plus 2pt minus 1pt}}
}{% if KOMA class
  \KOMAoptions{parskip=half}}
\makeatother
\usepackage{xcolor}
\IfFileExists{xurl.sty}{\usepackage{xurl}}{} % add URL line breaks if available
\IfFileExists{bookmark.sty}{\usepackage{bookmark}}{\usepackage{hyperref}}
\hypersetup{
  pdfauthor={Andrés Quiñones},
  hidelinks,
  pdfcreator={LaTeX via pandoc}}
\urlstyle{same} % disable monospaced font for URLs
\newif\ifbibliography
\usepackage{longtable,booktabs,array}
\usepackage{calc} % for calculating minipage widths
\usepackage{caption}
% Make caption package work with longtable
\makeatletter
\def\fnum@table{\tablename~\thetable}
\makeatother
\usepackage{graphicx}
\makeatletter
\def\maxwidth{\ifdim\Gin@nat@width>\linewidth\linewidth\else\Gin@nat@width\fi}
\def\maxheight{\ifdim\Gin@nat@height>\textheight\textheight\else\Gin@nat@height\fi}
\makeatother
% Scale images if necessary, so that they will not overflow the page
% margins by default, and it is still possible to overwrite the defaults
% using explicit options in \includegraphics[width, height, ...]{}
\setkeys{Gin}{width=\maxwidth,height=\maxheight,keepaspectratio}
% Set default figure placement to htbp
\makeatletter
\def\fps@figure{htbp}
\makeatother
\setlength{\emergencystretch}{3em} % prevent overfull lines
\providecommand{\tightlist}{%
  \setlength{\itemsep}{0pt}\setlength{\parskip}{0pt}}
\setcounter{secnumdepth}{-\maxdimen} % remove section numbering
\newlength{\cslhangindent}
\setlength{\cslhangindent}{1.5em}
\newlength{\csllabelwidth}
\setlength{\csllabelwidth}{3em}
\newlength{\cslentryspacingunit} % times entry-spacing
\setlength{\cslentryspacingunit}{\parskip}
\newenvironment{CSLReferences}[2] % #1 hanging-ident, #2 entry spacing
 {% don't indent paragraphs
  \setlength{\parindent}{0pt}
  % turn on hanging indent if param 1 is 1
  \ifodd #1
  \let\oldpar\par
  \def\par{\hangindent=\cslhangindent\oldpar}
  \fi
  % set entry spacing
  \setlength{\parskip}{#2\cslentryspacingunit}
 }%
 {}
\usepackage{calc}
\newcommand{\CSLBlock}[1]{#1\hfill\break}
\newcommand{\CSLLeftMargin}[1]{\parbox[t]{\csllabelwidth}{#1}}
\newcommand{\CSLRightInline}[1]{\parbox[t]{\linewidth - \csllabelwidth}{#1}\break}
\newcommand{\CSLIndent}[1]{\hspace{\cslhangindent}#1}
\usepackage{float} \usepackage{multicol} \usepackage{amsmath} \usepackage{graphicx} \usepackage{array} \usepackage{xcolor}
\ifLuaTeX
  \usepackage{selnolig}  % disable illegal ligatures
\fi

\title{Learning can mediate the evolution of\\
(cheap and costly) signals of quality}
\author{Andrés Quiñones}
\date{\hfill\break
\hfill\break
ISBE - Stockholm 2022\\
August 2 - 2020}

@@

\begin{frame}{Acknowledgements}
\protect\hypertarget{acknowledgements}{}
\begin{longtable}[]{@{}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}
  >{\centering\arraybackslash}p{(\columnwidth - 2\tabcolsep) * \real{0.5000}}@{}}
\toprule
\begin{minipage}[b]{\linewidth}\centering
\includegraphics[width=0.4\textwidth,height=\textheight]{../Images/redouan.jpg}
\end{minipage} & \begin{minipage}[b]{\linewidth}\centering
\includegraphics[width=0.55\textwidth,height=\textheight]{../Images/danielcadena.jpg}
\end{minipage} \\
\midrule
\endhead
\emph{R. Bshary} & \emph{D. Cadena} \\
\includegraphics[width=0.3\textwidth,height=\textheight]{../Images/UNINE_cmjn.jpg}
&
\includegraphics[width=0.3\textwidth,height=\textheight]{../Images/logo_largo.png} \\
\bottomrule
\end{longtable}
\end{frame}

\begin{frame}{Social interactions}
\protect\hypertarget{social-interactions}{}
\begin{block}{The need to match partners with actions}
\protect\hypertarget{the-need-to-match-partners-with-actions}{}
\begin{center}\includegraphics[width=0.4\linewidth]{../Images/sexSelec} \end{center}

\begin{center}\includegraphics[width=0.4\linewidth]{../Images/dominance} \end{center}
\end{block}
\end{frame}

\begin{frame}{The effect of communication}
\protect\hypertarget{the-effect-of-communication}{}
\begin{block}{Badge of status}
\protect\hypertarget{badge-of-status}{}
\begin{center}\includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_strong} \includegraphics[width=0.45\linewidth]{../Images/HouseSparrow_weak} \end{center}
\end{block}
\end{frame}

\begin{frame}{What about signals?}
\protect\hypertarget{what-about-signals}{}
\begin{block}{The handicap principle}
\protect\hypertarget{the-handicap-principle}{}
\begin{center}\includegraphics[height=0.35\textheight]{../Images/Amotz_Zahavi_profile} \includegraphics[height=0.35\textheight]{../Images/sexualSelection} \includegraphics[height=0.35\textheight]{../Images/Grafen} \end{center}

\begin{center}\includegraphics[height=0.35\textheight]{ISBE2022_files/figure-beamer/unnamed-chunk-4-1} \end{center}

(Zahavi 1975; Grafen 1990)
\end{block}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_0} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-1}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_1} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-2}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_2} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-3}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_3} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-4}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_5} \end{center}
\end{frame}

\begin{frame}{What about learning?}
\protect\hypertarget{what-about-learning-5}{}
\begin{center}\includegraphics[height=0.4\textheight]{../Images//pavlov} \end{center}

\begin{center}\includegraphics[width=16.76in,height=0.35\textheight]{../Images/learn_cartoon_6} \end{center}
\end{frame}

\begin{frame}{A model of communication in animal conflict}
\protect\hypertarget{a-model-of-communication-in-animal-conflict}{}
\vspace{-0.3cm}

\begin{block}{Conflict}
\protect\hypertarget{conflict}{}
\vspace{0.3cm}
\begin{columns}
\column{0.5\linewidth}
hawk-dove game
\tiny
\begin{center}
\begin{tabular}{ >{\centering\arraybackslash}p{0.2cm} | >{\centering\arraybackslash}p{2.5cm} | >{\centering\arraybackslash}p{0.8cm} }
& H & D \\ \hline
H & $p_w V\frac{-C}{2} + (1-p_w) \frac{-C}{2}$ & $V$ \\ \hline
V & $0$ & $\frac{V}{2}$\\
\end{tabular}
\end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-17-1} \end{center}

@@

\pause
\end{block}

\begin{block}{Communication}
\protect\hypertarget{communication}{}
\begin{columns}[T]

@@

\begin{center}\includegraphics[width=0.5\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-18-1} \end{center}

@@

\begin{center}\includegraphics[width=0.6\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-19-1} \end{center}

\end{columns}
\end{block}
\end{frame}

\begin{frame}{Learning under honest signalling}
\protect\hypertarget{learning-under-honest-signalling}{}
\begin{center}\includegraphics[width=1\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn} \end{center}
\end{frame}

@@

\begin{frame}{Learning mediates the evolution of badges of status
(handicaps)}
\protect\hypertarget{learning-mediates-the-evolution-of-badges-of-status-handicaps}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/betCostEvol1_/evolDyn0_betCost5} \end{center}
\end{frame}

\begin{frame}{Learning can mediate the evolution of Badges of Status}
\protect\hypertarget{learning-can-mediate-the-evolution-of-badges-of-status}{}
\begin{block}{Individual replicates: no badges}
\protect\hypertarget{individual-replicates-no-badges}{}
\begin{center}\includegraphics[width=19.44in,height=0.9\textheight]{../Simulations/betCostEvol1_/evolDyn5_betCost5} \end{center}
\end{block}
\end{frame}

\begin{frame}{The evolution of cheap badges of Status}
\protect\hypertarget{the-evolution-of-cheap-badges-of-status}{}
\begin{center}\includegraphics[width=0.9\linewidth]{../Simulations/nIntGroupNormQual_/evolDyn7_nIntGroup2000} \end{center}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized}{}
\vspace{-1cm}

\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever}{}
\begin{itemize}
\tightlist
\item
  Learning initial conditions
\end{itemize}

\includegraphics[width=0.45\linewidth]{../Simulations/alphaAct_/alphaAct0.4learnDyn}
\includegraphics[width=0.45\linewidth]{ISBE2022_files/figure-beamer/unnamed-chunk-24-2}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-1}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-1}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_1}
\end{block}
\end{frame}

\begin{frame}{Why would you want to be recognized?}
\protect\hypertarget{why-would-you-want-to-be-recognized-2}{}
\begin{block}{The peaceful, the aggressive and the clever}
\protect\hypertarget{the-peaceful-the-aggressive-and-the-clever-2}{}
\includegraphics[width=0.9\linewidth]{../Simulations/initAct_/indVarScatter_}
\end{block}
\end{frame}

\begin{frame}{Take-home messages}
\protect\hypertarget{take-home-messages}{}
\begin{block}{Costly signals}
\protect\hypertarget{costly-signals}{}
\begin{itemize}
\tightlist
\item
  Learning can mediate costly signals
\end{itemize}
\end{block}

\begin{block}{Cheap signals}
\protect\hypertarget{cheap-signals}{}
\begin{itemize}
\tightlist
\item
  Learning mediates the evolution of polymorphisms with ``honest'' and
  ``dishonest'' individuals
\item
  Cheap signals depend on the innate level of aggression (before
  learning) of individuals
\end{itemize}
\end{block}
\end{frame}

\begin{frame}{Questions?}
\protect\hypertarget{questions}{}
\begin{center}\includegraphics[height=0.8\textheight]{../Images/BizarroParrot} \end{center}
\end{frame}

\begin{frame}{References}
\protect\hypertarget{references}{}
\hypertarget{refs}{}
\begin{CSLReferences}{1}{0}
\leavevmode\vadjust pre{\hypertarget{ref-grafen_Biological_1990}{}}%
Grafen, Alan. 1990. {``Biological Signals as Handicaps.''} \emph{Journal
of Theoretical Biology} 144 (4): 517--46.
\url{https://doi.org/10.1016/S0022-5193(05)80088-8}.

\leavevmode\vadjust pre{\hypertarget{ref-zahavi_Mate_1975}{}}%
Zahavi, Amotz. 1975. {``Mate Selection\textemdash -{A} Selection for a
Handicap.''} \emph{Journal of Theoretical Biology} 53 (1): 205--14.
\url{https://doi.org/10.1016/0022-5193(75)90111-3}.

\end{CSLReferences}
\end{frame}

### 2022-07-20 manuscript/manuscript_1.0.Rmd
New presentation for ISBE2022

A somewhat ignored component of communication systems, in the context 
of aggressive interactions, is the cognitive aspects of the receiver module. 
Theoretical models often assume that Communication systems relying on badges of 
status to have reaction norms as their 
mechanistic underpinning [@Botero_Evolution_2010], with 
individuals using their own quality and the opponent's badge to determine 
whether to aggressively engage in contest. Reaction norms 
allow individuals to respond to the available information without a big
cognitive burden. That is at least in contrast to other information processing 
mechanisms like individual recognition. With individual recognition 
individuals associate cue of their peers to their quality. These association 
must be learn thoughout individuals lifes, thus it has the usual 
cognitive requirements of an associative learning process. An alternative view 
of badges of status is that individuals learn 
to react to them based on their experiences [@guilford_Receiver_1991], 
which would imply that receivers must learn to associate signals with 
the fighting ability of bearers just as in systems based on individual 
recognition. In cases where badges of status vary quantitatively 
(e.g. in size or intensity), fighting ability may increase monotonically 
with attributes of the badge and would be reinforced by every interaction, 
so in principle learning would be faster than in systems involving individual 
recognition in which the association between signals and their meaning would 
vary depending on the interacting partners. In any case, learning could be 
a central cognitive mechanism in both types of communication systems, 
but the role of learning in these contexts has not been thoroughly 
explored in the empirical nor theoretical literature.

>>>>

A somewhat ignored component of communication systems, in the context 
of aggressive interactions, is the cognitive aspects of the receiver module. 
Theoretical models often assume that Communication systems relying on badges of 
status to have reaction norms as their 
mechanistic underpinning [@botero_Evolution_2010], with 
individuals using their own quality and the opponent's badge to determine 
whether to aggressively engage in contest. Reaction norms 
allow individuals to respond to the available information without a big
cognitive burden. That is at least in contrast to other information processing 
mechanisms like individual recognition. With individual recognition 
individuals associate cue of their peers to their quality. These association 
must be learn thoughout individuals lifes, thus it has the usual 
cognitive requirements of an associative learning process. An alternative view 
of badges of status is that individuals learn 
to react to them based on their experiences [@guilford_Receiver_1991], 
which would imply that receivers must learn to associate signals with 
the fighting ability of bearers just as in systems based on individual 
recognition. In cases where badges of status vary quantitatively 
(e.g. in size or intensity), fighting ability may increase monotonically 
with attributes of the badge and would be reinforced by every interaction, 
so in principle learning would be faster than in systems involving individual 
recognition in which the association between signals and their meaning would 
vary depending on the interacting partners. In any case, learning could be 
a central cognitive mechanism in both types of communication systems, 
but the role of learning in these contexts has not been thoroughly 
explored in the empirical nor theoretical literature.
